---
title: "Heart_Attack_Analysis_&_Prediction_Dataset"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<div style="text-align:justify">

# Importing the dataset
```{r}
getwd()
heart_data = read.csv("heart.csv", sep = ",", header = TRUE)
```

# Structure Of Data
```{r}
str(heart_data)
```

```{r}
summary(heart_data)
```

```{r}
typeof(heart_data)
```

```{r}
class(heart_data)
```

```{r}
head(heart_data)
```

```{r}
age_club = heart_data$age[1:20]
```

```{r}
age_club
```

```{r}
class(age_club)
```

```{r}
sort(age_club)
```

```{r}
chol_club = heart_data$chol[1:10]
```

```{r}
chol_club
```

```{r}
sort(chol_club,decreasing = TRUE)
```

```{r}
class(heart_data$age)
```

```{r}
typeof(heart_data$age)
```

```{r}
mean(age_club)
```

```{r}
median(age_club)
```

```{r}
sum(age_club)
```

```{r}
cumsum(age_club)
```
```{r}
cumsum(age_club[1:10])
```

```{r}
cummax(age_club[1:10])
```

```{r}
rev(age_club)
```

```{r}
order(age_club[1:10])
```

```{r}
boxplot(heart_data$age)
```

```{r}
boxplot(heart_data$sex)
```

```{r}
boxplot(heart_data$cp)
```

```{r}
age1 <- filter(heart_data, heart_data$age > 50)
head(age1)
```


```{r}
age2 <- filter(heart_data, heart_data$chol < 150)
head(age2)
```

# Creating a Scatter Plot
To make a scatter plot,use plot() and pass it a vector of x values followed by a vector of y values:
```{r}
plot(heart_data$age,heart_data$chol)
````
The first part, ggplot(), tell it to create a plot object, and the second part, geom_point(), tells it to add a layer of points to the plot.
```{r}
library(ggplot2)

ggplot(heart_data, aes(x = age, y = chol)) +
  geom_point()
```


# Creating a Bar Graph
To make a bar graph of values,use barplot() and pass it a vector of values for the height of each bar and (optionally) a vector of labels for each bar. If the vector has names for the elements, the names will automatically be used as labels:

```{r}
barplot(heart_data$age, names.arg = heart_data$trtbps)
```
With ggplot2, you can get a similar result using geom_col(). To plot a bar graph of values, use geom_col(). Notice the difference in the output when the x variable is continuous and when it is discrete:
```{r}
ggplot(heart_data, aes(x = cp, y = oldpeak)) +
  geom_col()
ggplot(heart_data, aes(x = factor(cp), y = oldpeak)) +
  geom_col()
```

# Creating a Histogram
To make a histogram,use hist() and pass it a vector of values:
```{r}
hist(heart_data$age)

# Specify approximate number of bins with breaks
hist(heart_data$age, breaks = 10)
```
```{r}
ggplot(heart_data, aes(x = thalachh)) +
  geom_histogram()
ggplot(heart_data, aes(x = thalachh)) +
  geom_histogram(binwidth = 60)
```

# Making a Basic Bar Graph
Use ggplot() with geom_col() and specify what variables you want on the x- and y-axes:
```{r}
ggplot(heart_data, aes(x = oldpeak, y = cp)) +
  geom_col()
```

# Making a Bar Graphs of count
Use geom_bar() without mapping anything to y:
```{r}
ggplot(heart_data, aes(x = thalachh)) +
  geom_bar()
```

# Using Colors in Bar Graph


```{r}
heart_data$Gender <- factor(heart_data$sex,levels=c(0,1),labels=c("Male","Female"))
heart_data[1:15,]
```

```{r}
ggplot(heart_data, aes(x = age, y = chol, fill = Gender)) +
  geom_col()
```
```{r}
ggplot(data=heart_data,aes(x=sex,fill=Gender))+geom_bar()
ggplot(data=heart_data,aes(x=age,fill=Gender))+geom_histogram(col="black")
ggplot(data=heart_data,aes(x=cp,fill=Gender))+geom_bar()+
  theme(axis.text=element_text(size = 8))
ggplot(data=heart_data,aes(x=slp,fill=Gender))+geom_bar()
ggplot(data=heart_data,aes(x=exng,fill=Gender))+geom_bar()
```

</div>



